%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Laboratory Book
% LaTeX Template
% Version 1.0 (4/6/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Joan Queralt Gil (http://phobos.xtec.cat/jqueralt) using the labbook class by
% Frank Kuster (http://www.ctan.org/tex-archive/macros/latex/contrib/labbook/)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the labbook.cls file to be in the same directory as the
% .tex file. The labbook.cls file provides the necessary structure to create the
% lab book.
%
% The \lipsum[#] commands throughout this template generate dummy text
% to fill the template out. These commands should all be removed when 
% writing lab book content.
%
% HOW TO USE THIS TEMPLATE 
% Each day in the lab consists of three main things:
%
% 1. LABDAY: The first thing to put is the \labday{} command with a date in 
% curly brackets, this will make a new section showing that you are working
% on a new day.
%
% 2. EXPERIMENT/SUBEXPERIMENT: Next you need to specify what 
% experiment(s) and subexperiment(s) you are working on with a 
% \experiment{} and \subexperiment{} commands with the experiment 
% shorthand in the curly brackets. The experiment shorthand is defined in the 
% 'DEFINITION OF EXPERIMENTS' section below, this means you can 
% say \experiment{pcr} and the actual text written to the PDF will be what 
% you set the 'pcr' experiment to be. If the experiment is a one off, you can 
% just write it in the bracket without creating a shorthand. Note: if you don't 
% want to have an experiment, just leave this out and it won't be printed.
%
% 3. CONTENT: Following the experiment is the content, i.e. what progress 
% you made on the experiment that day.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------                               
\documentclass[fontsize=11pt, % Document font size
                             paper=a4, % Document paper type
                             twoside, % Shifts odd pages to the left for easier reading when printed, can be changed to oneside
                             captions=tableheading,
                             index=totoc,
                             hyperref]{labbook}
 
\usepackage[bottom=10em]{geometry} % Reduces the whitespace at the bottom of the page so more text can fit

\usepackage[english]{babel} % English language
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[utf8]{inputenc} % Uses the utf8 input encoding
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs

\usepackage[osf]{mathpazo} % Palatino as the main font
\linespread{1.05}\selectfont % Palatino needs some extra spacing, here 5% extra
\usepackage[scaled=.88]{beramono} % Bera-Monospace
\usepackage[scaled=.86]{berasans} % Bera Sans-Serif

\usepackage{booktabs,array} % Packages for tables

\usepackage{amsmath} % For typesetting math
\usepackage{graphicx} % Required for including images
\usepackage{etoolbox}
\usepackage[norule]{footmisc} % Removes the horizontal rule from footnotes
\usepackage{lastpage} % Counts the number of pages of the document

\usepackage[dvipsnames]{xcolor}  % Allows the definition of hex colors
\definecolor{titleblue}{rgb}{0.16,0.24,0.64} % Custom color for the title on the title page
\definecolor{linkcolor}{rgb}{0,0,0.42} % Custom color for links - dark blue at the moment

\addtokomafont{title}{\Huge\color{titleblue}} % Titles in custom blue color
\addtokomafont{chapter}{\color{OliveGreen}} % Lab dates in olive green
\addtokomafont{section}{\color{Sepia}} % Sections in sepia
\addtokomafont{pagehead}{\normalfont\sffamily\color{gray}} % Header text in gray and sans serif
\addtokomafont{caption}{\footnotesize\itshape} % Small italic font size for captions
\addtokomafont{captionlabel}{\upshape\bfseries} % Bold for caption labels
\addtokomafont{descriptionlabel}{\rmfamily}
\setcapwidth[r]{10cm} % Right align caption text
\setkomafont{footnote}{\sffamily} % Footnotes in sans serif

\deffootnote[4cm]{4cm}{1em}{\textsuperscript{\thefootnotemark}} % Indent footnotes to line up with text

\DeclareFixedFont{\textcap}{T1}{phv}{bx}{n}{1.5cm} % Font for main title: Helvetica 1.5 cm
\DeclareFixedFont{\textaut}{T1}{phv}{bx}{n}{0.8cm} % Font for author name: Helvetica 0.8 cm

\usepackage[nouppercase,headsepline]{scrpage2} % Provides headers and footers configuration
\pagestyle{scrheadings} % Print the headers and footers on all pages
\clearscrheadfoot % Clean old definitions if they exist

\automark[chapter]{chapter}
\ohead{\headmark} % Prints outer header

\setlength{\headheight}{25pt} % Makes the header take up a bit of extra space for aesthetics
\setheadsepline{.4pt} % Creates a thin rule under the header
\addtokomafont{headsepline}{\color{lightgray}} % Colors the rule under the header light gray

\ofoot[\normalfont\normalcolor{\thepage\ |\  \pageref{LastPage}}]{\normalfont\normalcolor{\thepage\ |\  \pageref{LastPage}}} % Creates an outer footer of: "current page | total pages"

% These lines make it so each new lab day directly follows the previous one i.e. does not start on a new page - comment them out to separate lab days on new pages
\makeatletter
\patchcmd{\addchap}{\if@openright\cleardoublepage\else\clearpage\fi}{\par}{}{}
\makeatother
\renewcommand*{\chapterpagestyle}{scrheadings}

% These lines make it so every figure and equation in the document is numbered consecutively rather than restarting at 1 for each lab day - comment them out to remove this behavior
\usepackage{chngcntr}
\counterwithout{figure}{labday}
\counterwithout{equation}{labday}

% Hyperlink configuration
\usepackage[
    pdfauthor={}, % Your name for the author field in the PDF
    pdftitle={Laboratory Journal}, % PDF title
    pdfsubject={}, % PDF subject
    bookmarksopen=true,
    linktocpage=true,
    urlcolor=linkcolor, % Color of URLs
    citecolor=linkcolor, % Color of citations
    linkcolor=linkcolor, % Color of links to other pages/figures
    backref=page,
    pdfpagelabels=true,
    plainpages=false,
    colorlinks=true, % Turn off all coloring by changing this to false
    bookmarks=true,
    pdfview=FitB]{hyperref}

\usepackage[stretch=10]{microtype} % Slightly tweak font spacing for aesthetics

%\setlength\parindent{0pt} % Uncomment to remove all indentation from paragraphs

\usepackage{mathrsfs, euscript} % Support command like \mathscr
\input{header_PhyWork_Pure.tex}% external physics command support
\graphicspath{{./pic/}}% set for path of pictures
%----------------------------------------------------------------------------------------
%	DEFINITION OF EXPERIMENTS
%----------------------------------------------------------------------------------------

% Template: \newexperiment{<abbrev>}[<short form>]{<long form>}
% <abbrev> is the reference to use later in the .tex file in \experiment{}, the <short form> is only used in the table of contents and running title - it is optional, <long form> is what is printed in the lab book itself

\newexperiment{example}[Example experiment]{This is an example experiment}
\newexperiment{example2}[Example experiment 2]{This is another example experiment}
\newexperiment{example3}[Example experiment 3]{This is yet another example experiment}

\newsubexperiment{subexp_example}[Example sub-experiment]{This is an example sub-experiment}
\newsubexperiment{subexp_example2}[Example sub-experiment 2]{This is another example sub-experiment}
\newsubexperiment{subexp_example3}[Example sub-experiment 3]{This is yet another example sub-experiment}

% Paper List


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title{\textcap{Research Notes \\[1cm]  
\textaut{\usefont{T1}{phv}{m}{sc} per aspera ad astra }}}

\author{
    \textaut{Yuan Hang}\\ \\ % Your name
}
\date{Date Compiled: \today \\ Data Began: March 25, 2017} % No date by default, add \today if you wish to include the publication date

\maketitle % Title page

\printindex
\tableofcontents % Table of contents
\newpage % Start lab look on a new page
%\listoffigures % List of figures
%\newpage % new page

\begin{addmargin}[4cm]{0cm} % Makes the text width much shorter for a compact look

\pagestyle{scrheadings} % Begin using headers

%----------------------------------------------------------------------------------------
%	LAB BOOK CONTENTS
%----------------------------------------------------------------------------------------
\labday{Saturday, March 25, 2017}
\experiment{101 Formulaic Alphas\cite{Kakushadze2015}}
When I saw this title, I thought this is an introductory paper to alphas as the 101 number usually indicated. It's really surpirsing that the author really wrote down 101 alphas. This kind of article is pretty different from common academic research papers. Many proprietary statement and hidden details. It's pretty interesting that this author even cited poems in the article. Anyway, as the first article to get started, I will record main points I get and list my quesitons below:
\begin{itemize}
\item Points
\begin{enumerate}
\item
Alpha is a pretty general meaning in this article, not just the alpha like the one in CAPM. The author gives a definition and I quote, ''An alpha is a combination of mathematical expressions, computer source code, and configuration parameters that can be used, in combination with historical data, to make predictions about future movements of various financial instruments.'' There are countless alphas could be constructed.(grow superexponentially?)
\item
General speaking, alpha signals could be based on mean-reversion or momentum or mixed.
\item
A ``delay-d'' alpha means if the alpha is traded today then the construction of this alpha involves data d days ago
\item
It's alphas are traded. Some characteristics of each alpha could be calculated, like shape ratio, turnover, cps, etc, from their trading data. (Characteristics of each product)
\item
The pair-wise relationship could be characterized by covariance matrix. However, study shows that variances of each alpha, which are extracted from historical data, are relatively stable.The off-diagonal elements are the focus to estimate.
\item
Using cross-sectional regressions, returns are strongly correlated with volatility V based on their data:
\begin{equation}
R\sim V^\gamma
\end{equation}
where $\gamma\approx 0.76$. Returns have no significant dependence on the turnover $T$.
\item To explore whether turnover could explain the correlation between alphas, multifactor risk model is applied. 
\begin{equation}
\Gamma_{ij}=\xi_i^2\delta_{ij}+\sum_{l,m}\Omega_{il}\Omega_{jm}\phi_{lm}
\end{equation}
I think the author applied a seemingly fancy skill to reachthe conclusion. I am still not sure why he did a symmetric tensor combinations.
\item
Result shows that linear and bilinear of log turnover have poor explanatory power of pair-wise correlations.
\item
Above conclusion does not necessarily mean the turnover adds no value in the risk factor model. It only shows that turnover does not appear to useful in modeling pair-wise alpha correlations.
\end{enumerate}
\item Questions
\begin{enumerate}
\item 
How to construct alpha systematically is not clear. If we want to construct alphas in billions, some clever methods needed.
\item
I need to study multi-factor risk model in detail
\item
How to understand three symmetrically constructed tensors are orthogonal to each other? Intuitively I agree. However, I need to understand it mathematically. I guess the answer should be found in statistics.
\item
Whether turnover adds value via the specific risk? Proprietary methods...
\end{enumerate}
\end{itemize}
\experiment{Performance v. Turnover: A Story by 4,000 Alphas\cite{Kakushadze2016}}
\experiment{Statistical arbitrage in the US equities market\cite{Avellaneda2010}}
\experiment{Active portfolio management\cite{grinold2000active}}
This review gives pedagogical introduction of Bose-Einstein condensates. It gives some overall background of BEC, especially the experiment realization. It mainly gives that how to realize periodic potential by optical lattice. The theory part starts from the linear case which is very common in condense matter physcis and discuss the beheavior of BEC governed by nonliear schrodinger equation. The techniques used for tackling the nonliear case is analogy to linear case such as weak periodic potential limit and tight-binding limit.
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\phantomsection
\bibliographystyle{unsrt}
\bibliography{QuantRef}

%----------------------------------------------------------------------------------------
\end{addmargin}
\end{document}